---
title: "Using 'Co-locationship' as an Alternative to Social Ties inPredictability of Human Mobility"
author: "Zexun CHEN"
date: "13/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("data.table")
library("dplyr")
library("ggplot2")
library("reshape2")
library("latex2exp")
library("magrittr")
library("ggpubr")
library(tikzDevice)
options(tikzMetricPackages = c("\\usepackage[utf8]{inputenc}",
    "\\usepackage[T1]{fontenc}", "\\usetikzlibrary{calc}",
    "\\usepackage{amssymb}"))

theme_set(
  theme_bw() +
    theme(legend.position = "top",
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          strip.background = element_blank(),
          panel.border = element_rect(colour = "black", fill = NA),
          legend.title = element_blank(),
          legend.spacing.x = unit(0.5, "char"),
          strip.text = element_text(size = 15),
          legend.text = element_text(
            face = "bold",
            size = 12
          ),
          axis.text = element_text(
            face = "bold",
            size = 12
          ),
          axis.title = element_text(
            face = "bold",
            size = 12
          ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
          )
)

colors_10 <- c(
  "#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd",
  "#8c564b", "#e377c2", "#7f7f7f", "#bcbd22", "#17becf"
)
catscale10 <- scale_colour_manual(values = colors_10)
catscale10_2 <- scale_fill_manual(values = colors_10)
```

## Dataset Check

First of all, we obtain the results from three datasets. and then generate plots of LZ entropy, predictability, Shannon entropy and the corresponding predictability.

```{r Extract results, echo=FALSE}
wp <- read.csv("final/wp-150/wp-dataset-basic.csv")
bk <- read.csv("final/bk-150/bk-dataset-basic.csv")
gw <- read.csv("final/gws-150/gws-dataset-basic.csv")

wp <- na.omit(wp)
bk <- na.omit(bk)
gw <- na.omit(gw)

wp$dataset <- "Weeplaces"
bk$dataset <- "BrightKite"
gw$dataset <- "Gowalla"
bk[, 1] <- sapply(bk[, 1], as.factor)
gw[, 1] <- sapply(gw[, 1], as.factor)

df <- do.call("rbind", list(wp, bk, gw))


df_entropy <- df %>% select(userid, Shannon.Entropy, LZ.Entropy, dataset)
df_entropy_melt <- melt(df_entropy,
  id.vars = c("userid", "dataset")
)

df_predictability <- df %>% select(userid, Shannon.Pi, LZ.Pi, dataset)
df_predictability_melt <- melt(df_predictability,
  id.vars = c("userid", "dataset")
)
```

### Focus on LZ entropy and datasets only

```{r LZ_entropy_Pi, echo=FALSE}
# df_together <- df %>% select(userid, LZ.Entropy, LZ.Pi, dataset)
# 
# df_together = rename(df_together, 
#                      'Entropy (bit)' = 'LZ.Entropy', 
#                      'Predictability' = 'LZ.Pi'
#                      )
# df_together_melt <- melt(df_together,
#                          id.vars = c("userid", "dataset")
# )


p_ent <- ggplot(df_entropy, aes(x = LZ.Entropy)) +
  geom_histogram(aes(fill = dataset),
                 alpha = 0.7, position = "identity", bins = 100
  ) +
  scale_fill_manual(
    values = colors_10[1:3]
  ) +
  # scale_color_manual(labels=c('A', 'B'), values = colors_10[1:2]) +
  labs(x = unname(TeX(c("Entropy  $\\hat{S}_A$ (bits)"))))

p_pred <- ggplot(df_predictability, aes(x = LZ.Pi)) +
  geom_histogram(aes(fill = dataset),
                 alpha = 0.7, position = "identity", bins = 100
  ) +
  scale_fill_manual(
    values = colors_10[1:3]
  ) +
  # scale_color_manual(labels=c('A', 'B'), values = colors_10[1:2]) +
  labs(x = unname(TeX(c("Predictability $\\Pi_{A}$"))))


ggarrange(
  p_ent, p_pred, labels = c("A", "B"), nrow = 1, ncol = 2,
  common.legend = TRUE, legend = "top"
)


# ggsave(
#   filename = "LZ_entropy_Pi_dataset.pdf", device = "pdf",
#   width = 9.90, height = 2.96,
#   path = "fig/"
# )

```

<!-- ### Entropy histgram (Shanno vs LZ) -->

<!-- ```{r Hist_entropy, echo=FALSE} -->
<!-- ggplot(df_entropy_melt, aes(x = value)) + -->
<!--   geom_histogram(aes(fill = variable), -->
<!--     alpha = 0.8, position = "identity", bins = 100 -->
<!--   ) + -->
<!--   theme( -->
<!--     legend.title = element_blank(), -->
<!--     legend.spacing.x = unit(0.5, "char"), -->
<!--     strip.text = element_text(size = 15), -->
<!--     legend.text = element_text( -->
<!--       face = "bold", -->
<!--       size = 12 -->
<!--     ), -->
<!--     axis.text = element_text( -->
<!--       face = "bold", -->
<!--       size = 12 -->
<!--     ), -->
<!--     axis.title = element_text( -->
<!--       face = "bold", -->
<!--       size = 12 -->
<!--     ), -->
<!--     # plot.title=element_text(face='bold', size=12,hjust = 0.5) -->
<!--   ) + -->
<!--   scale_fill_manual( -->
<!--     labels = unname(TeX(c("$S_{SN}", "$S_{LZ}"))), -->
<!--     values = colors_10[1:2] -->
<!--   ) + -->
<!--   # scale_color_manual(labels=c('A', 'B'), values = colors_10[1:2]) + -->
<!--   facet_wrap(~dataset) + -->
<!--   labs(x = "Entropy (bit)") -->

<!-- ggsave( -->
<!--   filename = "hist_entropy.pdf", device = "pdf", -->
<!--   width = 9.90, height = 2.66, -->
<!--   path = "fig/" -->
<!-- ) -->

<!-- ``` -->

<!-- ### Predictability histgram (Shanno vs LZ) -->

<!-- ```{r Hist_predictabiliy, echo=FALSE} -->
<!-- ggplot(df_predictability_melt, aes(x = value)) + -->
<!--   geom_histogram(aes(fill = variable), -->
<!--     alpha = 0.8, position = "identity", bins = 100 -->
<!--   ) + -->
<!--   theme( -->
<!--     legend.title = element_blank(), -->
<!--     legend.spacing.x = unit(0.5, "char"), -->
<!--     strip.text = element_text(size = 15), -->
<!--     legend.text = element_text( -->
<!--       face = "bold", -->
<!--       size = 12 -->
<!--     ), -->
<!--     axis.text = element_text( -->
<!--       face = "bold", -->
<!--       size = 12 -->
<!--     ), -->
<!--     axis.title = element_text( -->
<!--       face = "bold", -->
<!--       size = 12 -->
<!--     ), -->
<!--     # plot.title=element_text(face='bold', size=12,hjust = 0.5) -->
<!--   ) + -->
<!--   scale_fill_manual( -->
<!--     labels = unname(TeX(c("$\\Pi_{SN}", "$\\Pi_{LZ}"))), -->
<!--     values = colors_10[3:4] -->
<!--   ) + -->
<!--   facet_wrap(~dataset) + -->
<!--   labs(x = "Predictability") -->

<!-- ggsave( -->
<!--   filename = "hist_predictability.pdf", device = "pdf", -->
<!--   width = 9.90, height = 2.66, -->
<!--   path = "fig/" -->
<!-- ) -->

<!-- ``` -->


## Cross-entropy

This section is used to present all plots related to pairwise cross-entropy.

```{r Extract_CE_results, echo=FALSE}
## For 1-H Colocationship
# with quality control
wp_CE <- read.csv("temp_data/wp-150/wp-150-H/wp_CE_over1.csv")
bk_CE <- read.csv("temp_data/bk-150/bk-150-H/bk_CE_over1.csv")
gw_CE <- read.csv("temp_data/gws-150/gws-150-H/gws_CE_over1.csv")

# # # without quality control
# wp_CE <- read.csv("temp_data/wp-150/wp-150-H/wp_CE.csv")
# bk_CE <- read.csv("temp_data/bk-150/bk-150-H/bk_CE.csv")
# gw_CE <- read.csv("temp_data/gws-150/gws-150-H/gws_CE.csv")

wp_CE <- wp_CE[!is.na(wp_CE$CE_alter), ]
bk_CE <- bk_CE[!is.na(bk_CE$CE_alter), ]
gw_CE <- gw_CE[!is.na(gw_CE$CE_alter), ]


wp_CE$dataset <- "Weeplaces"
bk_CE$dataset <- "BrightKite"
gw_CE$dataset <- "Gowalla"

df_CE <- rbindlist(list(wp_CE, bk_CE, gw_CE))
# add a N_previous requirement M_previous >=150
df_CE <- within(df_CE, group[N_previous<150] <- 'useless')
df_CE$group %<>% factor(levels= c("useless","useful"))

df_CE_Rank1 <- df_CE %>% filter(group=='useful') %>% 
  group_by(userid_x, dataset) %>% 
  filter(row_number()==1)

df_CE_Rank5 <- df_CE %>% filter(group=='useful') %>% 
  group_by(userid_x, dataset) %>% 
  filter(row_number()==5)

df_CE_Rank10 <- df_CE %>% 
  group_by(userid_x, dataset) %>% filter(group=='useful') %>% 
  filter(row_number()==10)
## For Social Network
wp_true_CE <- read.csv("temp_data/wp-150/wp-true_CE.csv")
bk_true_CE <- read.csv("temp_data/bk-150/bk-true_CE.csv")
gw_true_CE <- read.csv("temp_data/gws-150/gws-true_CE.csv")


wp_true_CE <- wp_true_CE[!is.na(wp_true_CE$CE_alter), ]
bk_true_CE <- bk_true_CE[!is.na(bk_true_CE$CE_alter), ]
gw_true_CE <- gw_true_CE[!is.na(gw_true_CE$CE_alter), ]


wp_true_CE$dataset <- "Weeplaces"
bk_true_CE$dataset <- "BrightKite"
gw_true_CE$dataset <- "Gowalla"

df_true_CE <- rbindlist(list(wp_true_CE, bk_true_CE, gw_true_CE))
# add a N_previous requirement M_previous >=150
df_true_CE <- within(df_true_CE, group[N_previous<150] <- 'useless')
df_true_CE$group %<>% factor(levels= c("useless","useful"))

df_true_CE_Rank1 <- df_true_CE %>% filter(group=='useful') %>% 
  group_by(userid_x, dataset) %>% 
  filter(row_number()==1)

df_true_CE_Rank5 <- df_true_CE %>% filter(group=='useful') %>% 
  group_by(userid_x, dataset) %>% 
  filter(row_number()==5)

df_true_CE_Rank10 <- df_true_CE %>% filter(group=='useful') %>% 
  group_by(userid_x, dataset) %>% 
  filter(row_number()==10)


signif_CE5 <- df_CE_Rank5 %>% group_by(dataset)%>% 
  summarise(Mean=mean(CE_alter), Median=median(CE_alter), Std=sd(CE_alter))

signif_CE10 <- df_CE_Rank10 %>% group_by(dataset)%>% 
  summarise(Mean=mean(CE_alter), Median=median(CE_alter), Std=sd(CE_alter))

signif_true_CE5 <- df_true_CE_Rank5 %>% group_by(dataset)%>% 
  summarise(Mean=mean(CE_alter), Median=median(CE_alter), Std=sd(CE_alter))

signif_true_CE10 <- df_true_CE_Rank10 %>% group_by(dataset)%>% 
  summarise(Mean=mean(CE_alter), Median=median(CE_alter), Std=sd(CE_alter))

```

### All CE for both networks with useful rank-1 alter


```{r CE_Both_rank1, echo=FALSE}
p_CE_rank1 <- ggplot(df_CE_Rank1, aes(x = CE_alter)) +
  geom_histogram(aes(fill = dataset),
                 alpha = 0.6, position = "identity", bins = 100
  ) +
  # geom_density(aes(fill = dataset, color=dataset),
  #              alpha = 0.6, position = "identity"
  # ) +
  scale_fill_manual(
    values = colors_10[1:3]
  ) +
  scale_color_manual(values = colors_10[1:3]) +
  labs(x = unname(TeX(c("Cross-entropy  $\\hat{S}_{A|B}$ (bits)"))))


p_true_CE_rank1 <- ggplot(df_true_CE_Rank1, aes(x = CE_alter)) +
  geom_histogram(aes(fill = dataset),
                 alpha = 0.6, position = "identity", bins = 100
  ) +
  # geom_density(aes(fill = dataset, color=dataset),
  #              alpha = 0.6, position = "identity"
  # ) +
  scale_fill_manual(
    values = colors_10[1:3]
  ) +
  scale_color_manual(values = colors_10[1:3]) +
  labs(x = unname(TeX(c("Cross-entropy  $\\hat{S}_{A|B}$ (bits)"))))


ggarrange(
  p_ent, p_pred, p_true_CE_rank1, p_CE_rank1, 
  labels = c("A", "B", "C", "D"), nrow = 2, ncol = 2,
  common.legend = TRUE, legend = "top"
)


ggsave(
  filename = "Histogram_entropy_Pi_dataset.pdf", device = "pdf",
  width = 8.00, height =6.00,
  path = "fig/"
)
```

### All CE for both networks with useful rank-5 and rank-10 alters

```{r CE_Both_rank5_10, echo=FALSE}
p_CE_rank5 <- ggplot(df_CE_Rank5, aes(x = CE_alter)) +
  geom_histogram(aes(fill = dataset),
                 alpha = 0.6, position = "identity", bins = 70
  ) +
  geom_vline(data=signif_CE5, aes(xintercept = Mean, color = dataset),
             size=1.5) + 
  # geom_density(aes(fill = dataset, color=dataset),
  #              alpha = 0.6, position = "identity"
  # ) +
  scale_fill_manual(
    values = colors_10[1:3]
  ) +
  scale_color_manual(values = colors_10[1:3]) +
  labs(x = unname(TeX(c("Cross-entropy  $\\hat{S}_{A|B}$ (bits)"))))+
  xlim(0,10)

p_true_CE_rank5 <- ggplot(df_true_CE_Rank5, aes(x = CE_alter)) +
  geom_histogram(aes(fill = dataset),
                 alpha = 0.6, position = "identity", bins = 70
  ) + 
  geom_vline(data=signif_true_CE5, aes(xintercept = Mean, color = dataset),
             size=1.5) + 
  # geom_density(aes(fill = dataset, color=dataset),
  #              alpha = 0.6, position = "identity"
  # ) +
  scale_fill_manual(
    values = colors_10[1:3]
  ) +
  scale_color_manual(values = colors_10[1:3]) +
  labs(x = unname(TeX(c("Cross-entropy  $\\hat{S}_{A|B}$ (bits)"))))+
  xlim(0,10)


p_CE_rank10 <- ggplot(df_CE_Rank10, aes(x = CE_alter)) +
  geom_histogram(aes(fill = dataset),
                 alpha = 0.6, position = "identity", bins = 50
  ) +
  geom_vline(data=signif_CE10, aes(xintercept = Mean, color = dataset),
             size=1.5) + 
  # geom_density(aes(fill = dataset, color=dataset),
  #              alpha = 0.6, position = "identity"
  # ) +
  scale_fill_manual(
    values = colors_10[1:3]
  ) +
  scale_color_manual(values = colors_10[1:3]) +
  labs(x = unname(TeX(c("Cross-entropy  $\\hat{S}_{A|B}$ (bits)"))))+
  xlim(0,10)


p_true_CE_rank10 <- ggplot(df_true_CE_Rank10, aes(x = CE_alter)) +
  geom_histogram(aes(fill = dataset),
                 alpha = 0.6, position = "identity", bins = 50
  ) +
  geom_vline(data=signif_true_CE10, aes(xintercept = Mean, color = dataset),
             size=1.5) + 
  # geom_density(aes(fill = dataset, color=dataset),
  #              alpha = 0.6, position = "identity"
  # ) +
  scale_fill_manual(
    values = colors_10[1:3]
  ) +
  scale_color_manual(values = colors_10[1:3]) +
  labs(x = unname(TeX(c("Cross-entropy  $\\hat{S}_{A|B}$ (bits)")))) +
  xlim(0,10)


ggarrange(
  p_CE_rank5, p_true_CE_rank5, p_CE_rank10, p_true_CE_rank10,
  labels = c("A", "B", "C", "D"), nrow = 2, ncol = 2,
  common.legend = TRUE, legend = "top"
)


ggsave(
  filename = "Histogram_CE_5_10.pdf", device = "pdf",
  width = 8.00, height =6.00,
  path = "fig/"
)
```



### All CP and RCP with useful rank-1 alter

```{r CP_Both_rank1, echo=FALSE}
df_CE_Rank1$category <- 'Co-location Network'
df_CE_Rank1$meetup <- NULL
df_true_CE_Rank1$category <- 'Social Network'
df_Rank1 <- rbindlist(list(df_CE_Rank1, df_true_CE_Rank1))
df_Rank1$category <- as.factor(df_Rank1$category)
df_Rank1$Pi_alter_rate <- df_Rank1$Pi_alter / df_Rank1$Pi
df_Rank1 <- df_Rank1[df_Rank1$Pi_alter_rate < 2, ]

# # count how much points 
# df_Rank1[df_Rank1$Pi_alter_rate >= 2, ] %>% count(category)

p_CP_rank1_bk <- ggplot(df_Rank1[df_Rank1$dataset=='BrightKite',], aes(x = Pi_alter)) +
  geom_density(aes(fill = category, color=category),
               alpha = 0.6, position = "identity"
  ) +
  scale_colour_manual(
    values = colors_10[1:2]
  ) + 
  scale_fill_manual(
    values = colors_10[1:2]
  ) +
  labs(x = unname(TeX(c("Cross-predictability $\\Pi_{A|B}"))))

p_CP_rank1_gw <- ggplot(df_Rank1[df_Rank1$dataset=='Gowalla',], aes(x = Pi_alter)) +
  geom_density(aes(fill = category, color=category),
               alpha = 0.6, position = "identity"
  ) +
  scale_colour_manual(
    values = colors_10[1:2]
  ) + 
  scale_fill_manual(
    values = colors_10[1:2]
  ) +
  labs(x = unname(TeX(c("Cross-predictability $\\Pi_{A|B}"))))

p_CP_rank1_wp <- ggplot(df_Rank1[df_Rank1$dataset=='Weeplaces',], aes(x = Pi_alter)) +
  geom_density(aes(fill = category, color=category),
               alpha = 0.6, position = "identity"
  ) +
  scale_colour_manual(
    values = colors_10[1:2]
  ) + 
  scale_fill_manual(
    values = colors_10[1:2]
  ) +
  labs(x = unname(TeX(c("Cross-predictability $\\Pi_{A|B}"))))


p_RCP_rank1_bk <- ggplot(df_Rank1[df_Rank1$dataset=='BrightKite',], aes(x = Pi_alter_rate)) +
  geom_density(aes(fill = category, color=category),
               alpha = 0.6, position = "identity"
  ) +
  scale_colour_manual(
    values = colors_10[1:2]
  ) + 
  scale_fill_manual(
    values = colors_10[1:2]
  ) +
  labs(x = unname(TeX(c("Relative cross-predictability $\\Phi_{A|B}"))))

p_RCP_rank1_gw <- ggplot(df_Rank1[df_Rank1$dataset=='Gowalla',], aes(x = Pi_alter_rate)) +
  geom_density(aes(fill = category, color=category),
               alpha = 0.6, position = "identity"
  ) +
  scale_colour_manual(
    values = colors_10[1:2]
  ) + 
  scale_fill_manual(
    values = colors_10[1:2]
  ) +
  labs(x = unname(TeX(c("Relative cross-predictability $\\Phi_{A|B}"))))

p_RCP_rank1_wp <- ggplot(df_Rank1[df_Rank1$dataset=='Weeplaces',], aes(x = Pi_alter_rate)) +
  geom_density(aes(fill = category, color=category),
               alpha = 0.6, position = "identity"
  ) +
  scale_colour_manual(
    values = colors_10[1:2]
  ) + 
  scale_fill_manual(
    values = colors_10[1:2]
  ) +
  labs(x = unname(TeX(c("Relative cross-predictability $\\Phi_{A|B}"))))



ggarrange(
  p_CP_rank1_bk, p_CP_rank1_gw, p_CP_rank1_wp,
  p_RCP_rank1_bk, p_RCP_rank1_gw, p_RCP_rank1_wp,
  labels = c("A", "B", "C", "D", "E", "F"), nrow = 2, ncol = 3,
  common.legend = TRUE, legend = "top"
)


ggsave(
  filename = "Density_CP_RCP_Rank1.pdf", device = "pdf",
  width = 9.66, height =6.00,
  path = "fig/"
)
```

### CE for Co-location Network

```{r CE_CN, echo=FALSE}
f1 <- ggplot(df_CE, aes(x = CE_alter)) +
  geom_histogram(aes(fill = group),
    alpha = 0.8, position = "identity", bins = 100
  ) +
  theme(
    legend.title = element_blank(),
    legend.spacing.x = unit(0.5, "char"),
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +
  scale_fill_manual(
    # labels = unname(TeX(c("Useful", "$Useless"))),
    values = colors_10[8:9]
  ) +
  # scale_color_manual(labels=c('A', 'B'), values = colors_10[1:2]) +
  facet_wrap(~dataset, scales = "free") +
  labs(x = "LZ cross-entropy (bit)") 

print(f1)

ggsave(
  filename = "hist_CE_Np.pdf", device = "pdf",
  width = 9.90, height = 2.66,
  path = "fig/"
)
```

### CE for Social Network

```{r CE_True, echo=FALSE}
f2 <- ggplot(df_true_CE, aes(x = CE_alter)) +
  geom_histogram(aes(fill = group),
                 alpha = 0.8, position = "identity", bins = 100
  ) +
  theme(
    legend.title = element_blank(),
    legend.spacing.x = unit(0.5, "char"),
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +
  scale_fill_manual(
    # labels = unname(TeX(c("Useful", "$Useless"))),
    values = c(colors_10[8], colors_10[10])
  ) +
  # scale_color_manual(labels=c('A', 'B'), values = colors_10[1:2]) +
  facet_wrap(~dataset, scales = "free") +
  labs(x = "LZ cross-entropy (bit)")

print(f2)

ggsave(
  filename = "hist_true_CE_Np.pdf", device = "pdf",
  width = 9.90, height = 2.66,
  path = "fig/"
)

```

### Combine CE for Co-location Network and Social Network
```{r CE_combine, echo=FALSE}
# put p and q together
ggarrange(
  f1, f2, labels = c("A", "B"), nrow = 2, ncol = 1
  # common.legend = TRUE, legend = "top"
)

ggsave(
  filename = "hist_CLN_SRN_Np.pdf", device = "pdf",
  width = 9, height = 5,
  path = "fig/"
)

```

### Cross-predictability on useful alters only

```{r CP_useful, echo=FALSE}
df_CE_useful <- df_CE[df_CE$group == "useful", ]
df_true_CE_useful <- df_true_CE[df_true_CE$group == "useful", ]

df_CE_useful$category <- 'Co-location Network'
df_CE_useful$meetup <- NULL
df_true_CE_useful$category <- 'Social Network'
df_useful <- rbindlist(list(df_CE_useful, df_true_CE_useful))
```

```{r CP_useful_plot, echo=FALSE}
p <- ggplot(df_useful, aes(x = Pi_alter)) +
  geom_density(aes(fill = category,  color=category),
    alpha = 0.6, position = "identity"
  ) +
  theme(
    legend.title = element_blank(),
    legend.position="top",
    legend.text = element_text(size=12),
    legend.spacing.x = unit(0.5, "char"),
    strip.text = element_text(size = 15),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +
  scale_colour_manual(
    values = colors_10[1:2]
  ) + 
  scale_fill_manual(
    values = colors_10[1:2]
  ) +
  facet_wrap(~dataset, scales = "free") +
  labs(x = unname(TeX(c("Cross-predictability $\\Pi_{ego, alter}"))))
print(p)

ggsave(
  filename = "hist_cross_predictability_Np.pdf", device = "pdf",
  width = 9, height = 3,
  path = "fig/"
)
```

### Relative Cross-predictability on useful alters only

```{r relativeCCP_useful, echo=FALSE}
df_useful$Pi_alter_rate <- (df_useful$Pi_alter) / (df_useful$Pi)
df_useful <- df_useful[df_useful$Pi_alter_rate < 5, ]

q <- ggplot(df_useful, aes(x = Pi_alter_rate)) +
  geom_density(aes(fill = category, color=category),
    alpha = 0.6, position = "identity") +
  theme(
    legend.title = element_blank(),
    legend.position="top",
    legend.text = element_text(size=12),
    legend.spacing.x = unit(0.5, "char"),
    strip.text = element_text(size = 15),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +
  scale_colour_manual(
    values = colors_10[1:2]
  ) + 
  scale_fill_manual(
    values = colors_10[1:2]
  ) +
  facet_wrap(~dataset, scales = "free") +
  labs(x = unname(TeX(c("Relative cross-predictability $R_{alter|ego}"))))

print(q)

ggsave(
  filename = "hist_relative_cross_predictability_Np.pdf", device = "pdf",
  width = 9, height = 3,
  path = "fig/"
)
```

### Combine CCP and Retive CCP together

```{r combine_CCP_RCCP, echo=FALSE}
ggarrange(
  p, q, labels = c("A", "B"), nrow = 2, ncol = 1,
  common.legend = TRUE, legend = "top"
)

ggsave(
  filename = "density_CP_RCP_Np.pdf", device = "pdf",
  width = 9, height = 5,
  path = "fig/"
)

```

### Focus on useful both CE and PI over three datasets

```{r CE_Pi_Both, echo=FALSE}
df_useful_both <- df_useful %>% select(CE_alter, Pi_alter, dataset, category)

ggplot(df_useful_both, aes(x = CE_alter)) +
  geom_density(aes(fill = dataset, color=dataset),
               alpha = 0.6, position = "identity"
  ) +
  theme(
    legend.title = element_blank(),
    legend.spacing.x = unit(0.5, "char"),
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +
  scale_fill_manual(
    values = colors_10[1:3]
  ) +
  scale_color_manual(values = colors_10[1:3]) +
  facet_wrap(~category, scales = "free") + 
  labs(x = "LZ cross-entropy (bit)")

ggsave(
  filename = "density_CE_dataset_CLN_VS_SRN.pdf", device = "pdf",
  width = 9.00, height = 2.96,
  path = "fig/"
)

```


## Cumulative Cros-entropy
This section is used to generate all plots for CCP, CCE.

```{r Final_data_extract, echo=FALSE}
# theme_set(
#   theme_bw() +
#     theme(legend.position = "top")
# )

all_final <- read.csv('final/MeetupNp_Rank/150_all_category_MeetupNp.csv', 
                      stringsAsFactors = FALSE)

all_final$dataset[all_final$dataset=="Weeplace"]<-"Weeplaces"
all_final$category[all_final$category=="CB-1H-MFN"]<-"CB-1H-CN"
all_final$category[all_final$category=="CB-1D-MFN"]<-"CB-1D-CN"
all_final$category[all_final$category=="SW-24H-MFN"]<-"SW-24H-CN"
all_final$category[all_final$category=="TFN"]<-"Social Network"
```
### RCCP Co-location Network vs Social Network

```{r CCP_CN_vs_SN, echo=FALSE}
all_final_CN_SN <- subset(all_final, category %in% c("CB-1H-CN",
                                                "Social Network"))
all_final_CN_SN$category[all_final_CN_SN$category=="CB-1H-CN"]<-"Co-location Network"
                                                
all_final_CN_SN $category<- as.factor(all_final_CN_SN $category)
all_final_CN_SN $included <- as.factor(all_final_CN_SN $included)

Pi_alters <- ggplot(all_final_CN_SN , aes(x=included, y=mean, 
                      # shape=category,
                      color=category)) + 
  geom_point(size=3) +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    # legend.position = "none",
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +  catscale10 + 
  scale_y_continuous(labels = scales::percent) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,
                position=position_dodge(0.05)) + 
  facet_wrap(~dataset, scales = "free") + 
  labs(x = "Included number of alters", 
       y = unname(TeX(c("$\\Phi_{ego|alters}")))
  )

print(Pi_alters)

ggsave(
  filename = "ALL_relative_Pi_MeetupNp_part.pdf",
  device = "pdf",
  width = 9, height = 3.2,
  path = "fig/"
)

```

### RCCP different Co-location Networks

```{r CCP_CNs, echo=FALSE}
all_final_CNs <- subset(all_final, category %in% c("CB-1H-CN",
                                                "CB-1D-CN",
                                                "SW-24H-CN") 
)
all_final_CNs$category %<>% factor(levels= c("CB-1H-CN",
                                         "CB-1D-CN","SW-24H-CN"))
                                                
all_final_CNscategory<- as.factor(all_final_CNs$category)
all_final_CNs$included <- as.factor(all_final_CNs$included)

Pi_alters <- ggplot(all_final_CNs, aes(x=included, y=mean, 
                      # shape=category,
                      color=category)) + 
  geom_point(size=3) +
  theme(
    legend.title = element_blank(),
    # legend.position = "none",
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +  catscale10 + 
  scale_y_continuous(labels = scales::percent) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,
                position=position_dodge(0.05)) + 
  facet_wrap(~dataset, scales = "free") + 
  labs(x = "Included number of alters", 
       y = unname(TeX(c("$\\Phi_{ego|alters}$")))
  )

print(Pi_alters)

ggsave(
  filename = "ALL_relative_Pi_MeetupNp3.pdf",
  device = "pdf",
  width = 9, height = 3.2,
  path = "fig/"
)

```


## Similarity 
This section is used to generate all plots for similarity comparison.

```{r similarity_data, echo=FALSE}
wp_vip_sim <- read.csv('final/wp-150/wp_VIP_similarity_user_MeetupNp.csv', 
                       stringsAsFactors = FALSE)
wp_vip_sim$dataset <- 'Weeplaces'

bk_vip_sim <- read.csv('final/bk-150/bk_VIP_similarity_user_MeetupNp.csv', 
                       stringsAsFactors = FALSE)
bk_vip_sim$dataset <- 'BrightKite'

gw_vip_sim <- read.csv('final/gws-150/gws_VIP_similarity_user_MeetupNp.csv', 
                       stringsAsFactors = FALSE)
gw_vip_sim$dataset <- 'Gowalla'

df_vip_sim <- do.call("rbind", list(wp_vip_sim, bk_vip_sim, gw_vip_sim))
```

### Similarity (Co-location Network vs Social Network)

```{r similarity_vs2, echo=FALSE}
df_vip_sim_2 <- df_vip_sim %>% filter(Compare == "CB-1H-MFN vs TFN")
j1 <- ggplot(df_vip_sim_2, aes(x=dataset, y=Jaccard,
                       # shape=category,
                       fill=dataset
                       # color=Compare,
)) +
  geom_boxplot(width=0.5) +
  theme(
    legend.title = element_blank(),
    axis.text.x = element_text(vjust = 0.5, hjust=0.5),
    legend.position = "none",
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +  catscale10  + catscale10_2  +
  labs(x='', y='Local Jaccard Similarity')
print(j1)

# ggsave(
#   filename = "VIP_similarity_user_MeetupNp_part.pdf",
#   device = "pdf",
#   width = 2.45, height = 2.32,
#   path = "fig/"
# )


dataset = c('BrightKite', 'Gowalla', 'Weeplaces')
sim = c(0.48, 0.53, 0.5)
df_vip_sim_network <- data.frame(dataset, sim )
j2 <- ggplot(df_vip_sim_network, aes(x=dataset, y=sim, fill=dataset)) +
  geom_bar(stat="identity", width=0.5) +
  theme(
    legend.title = element_blank(),
    axis.text.x = element_text(vjust = 0.5, hjust=0.5),
    legend.position = "none",
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +  catscale10  + catscale10_2  +
  labs(x='', y='Global Jaccard Similarity')
print(j2)

# ggsave(
#   filename = "VIP_similarity_MeetupNp_part.pdf",
#   device = "pdf",
#   width = 2.45, height = 2.32,
#   path = "fig/"
# )

# combine them into one
ggarrange(
  j2, j1, labels = c("A", "B"), nrow = 1, ncol = 2
)

ggsave(
  filename = "VIP_similarity_Jaccard_MeetupNp_combined.pdf",
  device = "pdf",
  width = 5, height = 2.6,
  path = "fig/"
)
```


### Similarity (Different Co-location Networks)

```{r similarity_vs3, echo=FALSE}
df_vip_sim$Compare[df_vip_sim$Compare=="SW-24H-MFN vs CB-1D-MFN"]<-"SW-24H vs CB-1D"
df_vip_sim$Compare[df_vip_sim$Compare=="SW-24H-MFN vs CB-1H-MFN"]<-"SW-24H vs CB-1H"
df_vip_sim$Compare[df_vip_sim$Compare=="SW-24H-MFN vs TFN"]<-"SW-24H vs Social Network"
df_vip_sim$Compare[df_vip_sim$Compare=="CB-1D-MFN vs CB-1H-MFN"]<-"CB-1D vs CB-1H"
df_vip_sim$Compare[df_vip_sim$Compare=="CB-1D-MFN vs TFN"]<-"CB-1D vs Social Network"
df_vip_sim$Compare[df_vip_sim$Compare=="CB-1H-MFN vs TFN"]<-"CB-1H vs Social Network"

df_vip_sim <- subset(df_vip_sim, Compare %in% c("SW-24H vs CB-1D",
                                                "SW-24H vs CB-1H",
                                                "CB-1D vs CB-1H") 
                     )
df_vip_sim$Compare<- as.factor(df_vip_sim$Compare)

ggplot(df_vip_sim, aes(x=Compare, y=Jaccard,
                      # shape=category,
                      fill=Compare
                      # color=Compare,
                      )) +
  geom_boxplot() +
  theme(
    legend.title = element_blank(),
    axis.text.x = element_text(vjust = 1, hjust=0.5),
    legend.position = "none",
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +  catscale10  + catscale10_2 +
  facet_wrap(~dataset, nrow = 3,
             strip.position = 'right',
             scales = "free_y") +
  labs(x='', y='Jaccard Similarity')

ggsave(
  filename = "VIP_similarity_user_MeetupNp3.pdf",
  device = "pdf",
  width = 6.5, height = 4.5,
  path = "fig/"
)
```

## Distinct Location ratio

This section is used to generate all plotf about ODLR and CODLR.

```{r Extract_ODLR_COLDR, echo=FALSE}
vip_LR <- read.csv('final/MeetupNp_Rank/150_all_LR_MeetupNp.csv',
                   stringsAsFactors = FALSE)
vip_LR$dataset[vip_LR$dataset=="Weeplace"]<-"Weeplaces"
vip_LR$category[vip_LR$category=="CB-1H-MFN"]<-"CB-1H-CN"
vip_LR$category[vip_LR$category=="CB-1D-MFN"]<-"CB-1D-CN"
vip_LR$category[vip_LR$category=="SW-24H-MFN"]<-"SW-24H-CN"
vip_LR$category[vip_LR$category=="TFN"]<-"Social Network"

vip_CLR <- read.csv('final/MeetupNp_Rank/150_all_cumulative_LR_MeetupNp.csv', 
                    stringsAsFactors = FALSE)

vip_CLR$dataset[vip_CLR$dataset=="Weeplace"]<-"Weeplaces"
vip_CLR$category[vip_CLR$category=="CB-1H-MFN"]<-"CB-1H-CN"
vip_CLR$category[vip_CLR$category=="CB-1D-MFN"]<-"CB-1D-CN"
vip_CLR$category[vip_CLR$category=="SW-24H-MFN"]<-"SW-24H-CN"
vip_CLR$category[vip_CLR$category=="TFN"]<-"Social Network"
```


### ODLR and COLDR (Co-location Network vs Social Network)

```{r ODLR, echo=FALSE}

vip_LR_CN_SN <- vip_LR %>% filter((LR == "USLR") & 
                                    (category %in% c("CB-1H-CN", 
                                                     'Social Network')))
vip_LR_CN_SN$category[vip_LR_CN_SN$category=="CB-1H-CN"]<-"Co-location Network"


vip_LR_CN_SN$included <- as.factor(vip_LR_CN_SN$included)
vip_LR_CN_SN$category<- as.factor(vip_LR_CN_SN$category)

ODLR1 <- ggplot(vip_LR_CN_SN, aes(x=included, y=mean, 
                            # shape=category,
                            color=category)) + 
  geom_point(size=3) +
  theme(
    legend.title = element_blank(),
    # legend.position = "none",
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +  catscale10 + 
  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,
                position=position_dodge(0.05)) + 
  facet_wrap(~dataset, 
             scales = "free_y") +  
  labs(x = "Alter's Rank", 
       y = unname(TeX(c("$\\eta_{ego}(alter)")))
  )
print(ODLR1)

# CODLR
vip_CLR_CN_SN <- vip_CLR %>% filter((LR == "USLR") & 
                                    (category %in% c("CB-1H-CN", 
                                                     'Social Network')))
vip_CLR_CN_SN$included <- as.factor(vip_CLR_CN_SN$included)
vip_CLR_CN_SN$category<- as.factor(vip_CLR_CN_SN$category)

CODLR1 <- ggplot(vip_CLR_CN_SN, aes(x=included, y=mean, 
                              # shape=category,
                              color=category)) + 
  geom_point(size=3) +
  theme(
    legend.title = element_blank(),
    # legend.position = "none",
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +  catscale10 + 
  scale_y_continuous(labels = scales::percent) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,
                position=position_dodge(0.05)) + 
  facet_wrap(~dataset, 
             scales = "free_y") + 
  labs(x = "Included number of alters", 
       y = unname(TeX(c("$\\eta_{ego}(alters)")))
  )

print(CODLR1)

# Combine them into one plot
ggarrange(
  ODLR1, CODLR1, labels = c("A", "B"), nrow = 2, ncol = 1,
  common.legend = TRUE, legend = "top"
)

ggsave(
  filename = "VIP_CCP_VS_ODLR_CODLR_MeetupNp.pdf", device = "pdf",
  width = 9, height = 5,
  path = "fig/"
)

```

### ODLR and COLDR (Different Co-location Network)

```{r CODLR, echo=FALSE}
vip_LR_CNs <- vip_LR %>% filter((LR == "USLR") & 
                                  (category!="Social Network"))
vip_LR_CNs$category %<>% factor(levels= c("CB-1H-CN",
                                      "CB-1D-CN","SW-24H-CN"))
vip_LR_CNs $included <- as.factor(vip_LR_CNs$included)
vip_LR_CNs $category<- as.factor(vip_LR_CNs$category)

ODLR_all <- ggplot(vip_LR_CNs, aes(x=included, y=mean, 
                      # shape=category,
                      color=category)) + 
  geom_point(size=3) +
  theme(
    legend.title = element_blank(),
    # legend.position = "none",
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +  catscale10 + 
  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,
                position=position_dodge(0.05)) + 
  facet_wrap(~dataset, 
             scales = "free_y") +  
  labs(x = "Alter's Rank", 
       y = unname(TeX(c("$\\eta_{ego}(alter)")))
  )
print(ODLR_all)

# ggsave(
#   filename = "VIP_LR_MeetupNp_All.pdf",
#   device = "pdf",
#   width = 9, height = 3.2,
#   path = "fig/"
# )

# CODLR

vip_CLR_CNs <- vip_CLR %>% filter((LR == "USLR") & 
                                    (category!="Social Network"))
vip_CLR_CNs $category %<>% factor(levels= c("CB-1H-CN",
                                       "CB-1D-CN",
                                       "SW-24H-CN"))
vip_CLR_CNs$included <- as.factor(vip_CLR_CNs$included)
vip_CLR_CNs$category<- as.factor(vip_CLR_CNs$category)

CODLR_all <- ggplot(vip_CLR_CNs, aes(x=included, y=mean, 
                   # shape=category,
                   color=category)) + 
  geom_point(size=3) +
  theme(
    legend.title = element_blank(),
    # legend.position = "none",
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +  catscale10 + 
  scale_y_continuous(labels = scales::percent) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,
                position=position_dodge(0.05)) + 
  facet_wrap(~dataset, 
             scales = "free_y") + 
  labs(x = "Included number of alters", 
       y = unname(TeX(c("$\\eta_{ego}(alters)")))
  )

print(CODLR_all)

# ggsave(
#   filename = "VIP_cumulative_LR_MeetupNp_all.pdf",
#   device = "pdf",
#   width = 9, height = 3.2,
#   path = "fig/"
# )

# Combine them into one plot (cumulative)
ggarrange(
  ODLR_all, CODLR_all, labels = c("A", "B"), nrow = 2, ncol = 1,
  common.legend = TRUE, legend = "top"
)

ggsave(
  filename = "VIP_CCP_VS_ODLR_CODLR_MeetupNp_all.pdf", device = "pdf",
  width = 9, height = 5,
  path = "fig/"
)
```

## RCCP under Cross-validation
This section is used to generate plots for Relative cumulative cross-predictability by including randomly-selected alters in qualifiedCB-1H-CN and Social Network network.

```{r RCCP_CV, echo=FALSE}

vip_CV <- read.csv('final/MeetupNp_Rank/150_all_CV_MeetupNp.csv', 
                   stringsAsFactors = FALSE)


vip_CV$dataset[vip_CV$dataset=="Weeplace"]<-"Weeplaces"
vip_CV$category[vip_CV$category=="Friendship"]<-"Social Network"
vip_CV$category[vip_CV$category=="CB-1H-CN"]<-"Co-location Network"
vip_CV$included <- as.factor(vip_CV$included)

ggplot(vip_CV, aes(x=included, y=mean, 
                   # shape=category,
                   color=category)) + 
  geom_point(size=3) +
  theme(
    legend.title = element_blank(),
    # legend.position = "none",
    strip.text = element_text(size = 15),
    legend.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.text = element_text(
      face = "bold",
      size = 12
    ),
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    # plot.title=element_text(face='bold', size=12,hjust = 0.5)
  ) +  catscale10 + 
  scale_y_continuous(labels = scales::percent) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,
                position=position_dodge(0.05)) + 
  facet_wrap(~dataset, 
             scales = "free_y") + 
  labs(x = "Included number of alters", 
       y = unname(TeX(c("$\\Phi_{ego|alters}")))
       )

ggsave(
  filename = "VIP_CV_MeetupNp.pdf", device = "pdf",
  width = 9, height = 3.2,
  path = "fig/"
)

```

## Regression Analysis
This section is used to generate plots regression analysis.


### Weeplaces, Rank 10 only
```{r WP_RegressionRank10, echo=FALSE}
# ONLY WEEPLACE, RANK=10
df_all <- read.csv("final/MeetupNp_Rank/150_all_MeetupNp_CODLR_CCP.csv",
                   stringsAsFactors = FALSE)
df_all$category[df_all$category=="CB-1H-MFN"]<-"Co-location Network"
df_all$category[df_all$category=="TFN"]<-"Social Network"
Network<- subset(df_all, subset= (Included==10 & 
                                     category%in%c('Co-location Network', 
                                                   'Social Network') 
                                   & (dataset=='Weeplace')))
Network$Included <- as.factor(Network$Included)
Network$category <- as.factor(Network$category)

ggscatter(Network, x = "USLR", y = "Pi_alters_ratio", color='category',
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE,
          cor.coeff.args = list(method = "pearson", label.x.npc = 0.2, label.y.npc = 0.04),
          xlab = unname(TeX(c("$\\eta_{ego}(alters)"))),
          ylab = unname(TeX(c("$\\Phi_{ego|alters}")))) +
  theme(
    legend.title = element_blank(),
    strip.text = element_blank()
    # legend.position = "right",
    # strip.text.x = element_text(size = 8),
    # strip.text.y = element_blank(),
  )+
  scale_x_continuous(labels = scales::percent) +  catscale10 + catscale10_2 + 
  facet_wrap(~category,
             nrow = 1,
             ncol = 2,
             scales = 'free_y',
             # strip.position="right"
  )

# ggsave(
#   filename = "VIP_MeetupNp_CODLR_CCP_Weeplace.pdf", device = "pdf",
#   width = 5, height = 3,
#   path = "fig/"
# )
```

### Weeplaces, Rank 1--10, Social Network
```{r WP_RegressionRank1_10_SN, echo=FALSE}
## focus on weeplace dataset
SN_H <-subset(df_all, subset= (category=='Social Network' & 
                                  dataset=='Weeplace'))
SN_H$Included <- as.factor(SN_H$Included)

ggscatter(SN_H, x = "USLR", y = "Pi_alters_ratio", color = colors_10[2],
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, 
          cor.coeff.args = list(method = "pearson"),
          xlab = unname(TeX(c("$\\eta_{ego}(alters)"))),
          ylab = unname(TeX(c("$\\Phi_{ego|alters}")))) +
  theme(strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA),
        legend.title = element_blank(),
    # legend.position = "none",
    # strip.text.x = element_text(size = 8),
    # strip.text = element_blank(),
  )+
  scale_x_continuous(labels = scales::percent)+
  facet_wrap(~Included,
             nrow = 3,
             ncol = 4,
             scales = 'free_y',
             # strip.position="right"
  )

ggsave(
  filename = "VIP_MeetupNp_CODLR_CCP_wp_TFN.pdf",
  device = "pdf",
  width = 9.39, height = 6.24,
  path = "fig/"
)
```

### Weeplaces, Rank 1--10, Co-location Network
```{r WP_RegressionRank1_10_CN, echo=FALSE}
## focus on weeplace dataset
CN_H <-  subset(df_all, subset= (category=='Co-location Network' & 
                                    dataset=='Weeplace'))

CN_H$Included <- as.factor(CN_H$Included)

ggscatter(CN_H, x = "USLR", y = "Pi_alters_ratio", color = colors_10[1],
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, 
          cor.coeff.args = list(method = "pearson"),
          xlab = unname(TeX(c("$\\eta_{ego}(alters)"))),
          ylab = unname(TeX(c("$\\Phi_{ego|alters}")))) +
  theme(strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA),
        legend.title = element_blank(),
    # legend.position = "none",
    # strip.text.x = element_text(size = 8),
    # strip.text = element_blank(),
  )+
  scale_x_continuous(labels = scales::percent)+
  facet_wrap(~Included,
             nrow = 3,
             ncol = 4,
             scales = 'free_y',
             # strip.position="right"
  )

ggsave(
  filename = "VIP_MeetupNp_CODLR_CCP_wp_H_MFN.pdf",
  device = "pdf",
  width = 9.39, height = 6.24,
  path = "fig/"
)

```